Automated topic naming to support analysis of software maintenance activities

### 2010-08-20 icse/icse2011.tex
updated process model, changed subsubsec to simpler heading for space

\section{Introduction}

Topics in software engineering practice refer to specific shared threads of discussions between project stakeholders. These topics can include particular requirements, maintenance requests, bug fixes or other software engineering tasks. %NEIL: define topic specifically as akin to email 'thread'. It sounded too vague. Also changed from 'developers' to 'stakeholders' because developers sounds too coding oriented. Our work could apply to testers, users, etc.
While addressing a topic of development, stakeholders often produce or modify multiple development artifacts.
%
These artifacts can include source code, bug reports, revisions to source code, and test cases. 
%
Topics are typically latent, i.e., not explicitly named, and can be in several potential states: they may not be immediately resolved, they may re-occur, yet others are only dealt with briefly  (e.g., a bug report that is closed).
% semi-automatically sounds too uncertain. I think the introduction can be more muscular and bold. Don't give the reviewer any room to start doubting.

@@

This paper begins by introducing labelled topic extraction (Section \ref{sec:wordlist}). We show that these labels with their topics can be learned and used to classify other data-sets, either without training (Section \ref{sec:unsuplabelling}), or with training (Section \ref{sec:suplearn}). We then present visualizations of named topics and their trends over time to aid communication and analysis. We use an exploratory case study of two open source database systems to show how named topics can be compared between projects  (Section \ref{sec:analysis}). The paper concludes with a discussion of limitations (Section \ref{sec:limit}) and related work (Section \ref{sec:related}).

@@

\subsubsection{Analysis of the unsupervised labelling}

Based on the labels, and our manual topic labelling, we compared the results of the unsupervised word matching approach. 
For each quality we assessed whether unsupervised labels matches the manual annotations.
Figure \ref{fig:maxdb-unsup-results} shows our results for MaxDB and MySQL. 
Our performance is measured using the \emph{ROC} (Receiver Operating Characteristic) area-under-curve value~\cite{Fawcett2006861}. 
ROC values provide a score, similar to school letter-grades (A is 0.9, C is 0.6), reflecting how well a particular learner performed for the given data. 
ROC maps to the more familiar concepts of precision/sensitivity and recall/specificity: it plots the true positive rate (sensitivity) versus the false positive rate (1 - specificity). 
A perfect learner has a ROC value of 1.0, reflecting perfect recall and precision. 
A ROC result of 0.5 would be equivalent to a random learner (that is, issuing as many false positives as true positives). 
The AUC of a classifier is equivalent to the probability that the classifier will rank a randomly chosen positive instance higher than a randomly chosen negative instance.

@@

\subsection{Supervised labelling}
\label{sec:suplearn}
Supervised labelling requires expert analysis of the correct word to assign to a topic. %In order to validate how effective these word-bag approaches to topic labelling would be we created a validation data set.

@@

\subsubsection{Analysis of the supervised labelling}
\label{sec:suplabelling}
Because our data-set was of word counts we expected Bayesian techniques, often used in spam filtering, to perform well. 
We tried other learners that WEKA~\cite{weka09} provides: rule learners, decision tree learners, vector space learners, and support vector machines.  
Figure \ref{fig:best-learn-per-tag} shows the performance of the best performing learner per label. 
 We considered the best learner for a label to be the learner which had the highest ROC value for that label. 
Figure \ref{fig:best-learn-per-tag} uses the ZeroR learner as a baseline, a common practice in machine learning,
as ZeroR naively chooses the largest category all of the time. 
ZeroR occasionally outperforms other learners; for labels which are not as common, this is to be expected because any miscategorization will hurt accuracy. 
This is why we use ROC values, instead of accuracy, as they can better represent performance on labels which are not applicable to the majority of samples.

@@

Figure~\ref{fig:mulan} presents the results of Mulan's best multi-label learners for our data. 
Calibrated Label Ranking (CLR) is a learner that builds two layers, the first layer determines if an entity should be labelled, while the second layer determines what labels should be assigned.
The Hierarchy Of Multi-label classifiERs (HOMER) and Binary Relevance (BR) act as a hierarchy of learners: BR is flat, while HOMER tries to build a deeper hierarchy to build a more accurate learner~\cite{mulan}. 
These classifiers performed better than other multi-label classifiers. 
They have the best micro and macro ROC scores, although their results are comparable to the naive Bayesian learners we used in Section \ref{sec:suplearn}.
\todo[inline]{discuss this similarity in more detail}

@@

With respect to the questions raised in section \ref{sec:suplearn}:

@@

\begin{comment}
 shared-report.sh ; cat output/shared-j48-words

      2 bug
      2 code
      2 compiler
      2 database
      2 Delete_
      2 HP_UX
      2 memory
      2 missing
      2 monty_mysql_com
      2 monty_mysql_fi
      2 problems
      2 Removed
      2 work__home_bk_mysql
      4 4_0
      4 Add
      4 added
      4 Changed
      4 problem
      6 Added
      6 test

\end{comment}

@@

\begin{comment}
%We maintain that these results require more substantive manipulation before being reported to, for example, management. Like any large-scale data analysis project, it requires skill to derive the implications. Hooking the backend results directly to a reporting tool is unlikely to produce useful results.

% There has been an explosion of interest in mining OSS repositories. Godfrey and Tu \cite{godfrey00} were among the first to use this data to assess software evolution. They discussed how well the growth of Linux was predicted by laws that Lehman and colleagues \cite{lehman85} proposed. More recently, Herraiz et al. \cite{herraiz07icsm} predicted OSS growth using time series analysis. Like us, they refer to release windows as a useful unit of analysis. 
\end{comment}

@@

@@

%XXX can save space here!
%\section{Appendix}
\appendix

\end{document}
% \begin{comment}
% A quick mind dump before I forget:
% * portability was very popular
% * there were many instances of concurrency
% * There were often topics of crap commits with no comment
% * might need more than the top words to compare
% * Things like tests were noticable more by file type
% * Configuration management is not part of the software quality ontology?
% * I didn't tag none I tagged unknown, so that's some inconsistency between us
% * There were a lot of copyright changes in mysql
% * mysql had optimizer module which did not mean optimization
% * I tried to assign reliability/bug for reliability bugs
%   and Functionality/Correctness for fixes
% * Some security changes came later
% * Mysql 3.23 transitioned from a project being developed to
%   a project being maintained, more frequent back-port bug-fixes
% \end{comment}
% % a rough sketch 
% The size of these artifacts is cumbersome for a developer or stakeholder to comprehend, thus they often have to be ``chunked'', grouped, modularized, organized and finally labelled.
% Even more difficult is to pull together tangible trails or interests that pervade these artifacts.
% These interests or topics are only really visible by analyzing multiple artifacts.
% Other researchers have focused on extracting these topics from development artifacts, but often their approach leaves the organization or the labelling step to the user.
% What we propose is to 
% In this paper, we seek to automatically extract these interests, or topics that link artifacts such as source control commits and label them.

>>>>

\section{Introduction}
Topics in software engineering practice refer to specific shared threads of discussions between project stakeholders. 
These topics can include particular requirements, maintenance requests, bug fixes or other software engineering tasks. %NEIL: define topic specifically as akin to email 'thread'. It sounded too vague. Also changed from 'developers' to 'stakeholders' because developers sounds too coding oriented. Our work could apply to testers, users, etc.
While addressing a topic of development, stakeholders often produce or modify multiple development artifacts.
%
These artifacts can include source code, bug reports, revisions to source code, and test cases. 
%
Topics are typically latent, i.e., not explicitly named, and can be in several potential states: they may not be immediately resolved, they may re-occur, yet others are only dealt with briefly  (e.g., a bug report that is closed).
% semi-automatically sounds too uncertain. I think the introduction can be more muscular and bold. Don't give the reviewer any room to start doubting.

@@

This paper begins by introducing labelled topic extraction (Section \ref{sec:wordlist}). We show that these labels with their topics can be learned and used to classify other data-sets, either without training (Section \ref{sec:unsuplabelling}), or with training (Section \ref{sec:suplabelling}). We then present visualizations of named topics and their trends over time to aid communication and analysis. We use an exploratory case study of two open source database systems to show how named topics can be compared between projects  (Section \ref{sec:analysis}). The paper concludes with a discussion of limitations (Section \ref{sec:limit}) and related work (Section \ref{sec:related}).

@@

\textbf{Analysis of the unsupervised labelling} -- Based on the labels, and our manual topic labelling, 
we compared the results of the unsupervised word matching approach. 
For each quality we assessed whether unsupervised labels matches the manual annotations.
Figure \ref{fig:maxdb-unsup-results} shows our results for MaxDB and MySQL. 
Our performance is measured using the \emph{ROC} (Receiver Operating Characteristic) area-under-curve value~\cite{Fawcett2006861}. 
ROC values provide a score, similar to school letter-grades (A is 0.9, C is 0.6), reflecting how well a particular learner performed for the given data. 
ROC maps to the more familiar concepts of precision/sensitivity and recall/specificity: it plots the true positive rate (sensitivity) versus the false positive rate (1 - specificity). 
A perfect learner has a ROC value of 1.0, reflecting perfect recall and precision. 
A ROC result of 0.5 would be equivalent to a random learner (that is, issuing as many false positives as true positives). 
The AUC of a classifier is equivalent to the probability that the classifier will rank a randomly chosen positive instance higher than a randomly chosen negative instance.

@@

\subsection{Supervised labelling}
\label{sec:suplabelling}
Supervised labelling requires expert analysis of the correct word to assign to a topic. %In order to validate how effective these word-bag approaches to topic labelling would be we created a validation data set.

@@

\textbf{Analysis of the supervised labelling} -- 
% \label{sec:suplabelling}
Because our data-set was of word counts we expected Bayesian techniques, often used in spam filtering, to perform well. 
We tried other learners that WEKA~\cite{weka09} provides: rule learners, decision tree learners, vector space learners, and support vector machines.  
Figure \ref{fig:best-learn-per-tag} shows the performance of the best performing learner per label. 
 We considered the best learner for a label to be the learner which had the highest ROC value for that label. 
Figure \ref{fig:best-learn-per-tag} uses the ZeroR learner as a baseline, a common practice in machine learning,
as ZeroR naively chooses the largest category all of the time. 
ZeroR occasionally outperforms other learners; for labels which are not as common, this is to be expected because any miscategorization will hurt accuracy. 
This is why we use ROC values, instead of accuracy, as they can better represent performance on labels which are not applicable to the majority of samples.

@@

Figure~\ref{fig:mulan} presents the results of Mulan's best multi-label learners for our data. 
Calibrated Label Ranking (CLR) is a learner that builds two layers, the first layer determines if an entity should be labelled, while the second layer determines what labels should be assigned.
The Hierarchy Of Multi-label classifiERs (HOMER) and Binary Relevance (BR) act as a hierarchy of learners: BR is flat, while HOMER tries to build a deeper hierarchy to build a more accurate learner~\cite{mulan}. 
These classifiers performed better than other multi-label classifiers. 
They have the best micro and macro ROC scores, although their results are comparable to the naive Bayesian learners we used in Section \ref{sec:suplabelling}.
\todo[inline]{discuss this similarity in more detail}

@@

With respect to the questions raised in section \ref{sec:suplabelling}:

@@

@@

@@

\appendix

\end{document}

% \begin{comment}
%  shared-report.sh ; cat output/shared-j48-words 
% 
%       2 bug
%       2 code
%       2 compiler
%       2 database
%       2 Delete_
%       2 HP_UX
%       2 memory
%       2 missing
%       2 monty_mysql_com
%       2 monty_mysql_fi
%       2 problems
%       2 Removed
%       2 work__home_bk_mysql
%       4 4_0
%       4 Add
%       4 added
%       4 Changed
%       4 problem
%       6 Added
%       6 test
% 
% \end{comment}

% \begin{comment}
% A quick mind dump before I forget:
% * portability was very popular
% * there were many instances of concurrency
% * There were often topics of crap commits with no comment
% * might need more than the top words to compare
% * Things like tests were noticable more by file type
% * Configuration management is not part of the software quality ontology?
% * I didn't tag none I tagged unknown, so that's some inconsistency between us
% * There were a lot of copyright changes in mysql
% * mysql had optimizer module which did not mean optimization
% * I tried to assign reliability/bug for reliability bugs
%   and Functionality/Correctness for fixes
% * Some security changes came later
% * Mysql 3.23 transitioned from a project being developed to
%   a project being maintained, more frequent back-port bug-fixes
% \end{comment}
% % a rough sketch 
% The size of these artifacts is cumbersome for a developer or stakeholder to comprehend, thus they often have to be ``chunked'', grouped, modularized, organized and finally labelled.
% Even more difficult is to pull together tangible trails or interests that pervade these artifacts.
% These interests or topics are only really visible by analyzing multiple artifacts.
% Other researchers have focused on extracting these topics from development artifacts, but often their approach leaves the organization or the labelling step to the user.
% What we propose is to 
% In this paper, we seek to automatically extract these interests, or topics that link artifacts such as source control commits and label them.

@@

%XXX can save space here!
%\section{Appendix}
